$p$-adic precision

### 2014-02-19 padicprec.tex

\begin{prop} \label{prop : legendre transform}
If $f$ and $g$ are two real convex functions such that $f \geq g,$ then $f^* \leq g^*.$
Furthermore, the slopes of $f^*$ corresponds to vertices of $f$.
\end{prop}

@@

\begin{prop} \label{prop : locanalyticfinitedim}
If $f$ is a locally analytic map $K^n \rightarrow K^m$, with $K$ a $p$-adic field, if $C,$ $\rho$ and $\varepsilon$ are as above. It is enough to work with the Newton polygon $\NP_F$ of $F(t) = \sum_{k\geq 0}^{+\infty} \interleave f^{(k+1)}(0) \interleave  t^k \in \mathbb{R}[[t]]$ : let $r$ be such that $\NP_F^* \left( \log_p r - \frac{1}{p-1} \right) \leq \log_p \varepsilon.$ Then $r$ is enough for lemma \ref{lem:main}. 
\end{prop}
\begin{proof}
Same as before, with $L_n=\frac{f^{(n)}(0)}{n!}$ and Legendre formula. The result follows \textit{mutatis mutandis}.
\end{proof}

>>>>

\begin{prop} \label{prop : legendre transform}
Slopes of $f^*$ corresponds to extreme points of $f$.
\end{prop}

@@

\begin{prop} \label{prop : locanalyticfinitedim}
If $f$ is a locally analytic map $K^n \rightarrow K^m$, with $K$ a $p$-adic field, if $C,$ $\rho$ and $\varepsilon$ are as above. It is enough to work with the Newton polygon $NP_F$ of $F(t) = \sum_{k\geq 0}^{+\infty} \interleave f^{(k+1)}(0) \interleave  t^k \in \mathbb{R}[[t]]$ : let $\delta$ be such that $NP_F^* \left( \log_p \delta - \frac{1}{p-1} \right) \leq \log_p \varepsilon.$ Then $\delta$ is enough for lemma \ref{lem:main}. 
\end{prop}
\begin{proof}
Same as before, with $L_n=\frac{f^{(n)}(0)}{n!}$ and Legendre formula. The result follows \textit{mutatis mutandis}.
\end{proof}
